Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-04-25 lqg-strings.tex
minor wording changes in bimetric section of main file and sketching

Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{B P}}{\delta g^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}}
\end{multline}

\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}} \right) ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{B P}}{\delta h^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}}
\end{multline}
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} - \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}} \right) ,
\end{equation}
with
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If $S_{int} = 0$ and the auxiliary metrics $g_{a b}$ and $h_{a b}$ coincide with the induced metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, then the action\eqref{eqn:bimetric-Polyakov} reduces to
\begin{equation} \label{eqn:reduced-bimetric-action}
	S' _{B P} = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
\end{equation}
which, if $T' = - T k \Delta / 2$ and $h = g^{-1}$ becomes precisely the Nambu-Goto area corrected action\eqref{eqn:modified-NG-action}. The condition $h = g^{-1}$ can be achieved by
\begin{equation} \label{eqn:h=SgS}
	h_{a b} = S_{a c} g^{c d} S_{d b} ,
\end{equation}
where $S \in \mathrm{SL}(2 , \mathbb{C})$. The fact that we require $S = S^{\dagger}$ for $h$ to be real and symmetric restricts $S$ to be a boost. By requiring that the induced metric by $H_{\mu \nu}$ be equal to\eqref{eqn:h=SgS}, we get
\begin{equation} \label{eqn:H-from-SgS}
	\partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} = S_{a c} g^{c d} S_{d b}
\end{equation}
from which follows
\begin{equation}
	H_{\mu \nu} = \frac{1}{8 (- g)} (\Tr (S \varepsilon))^2 G_{\mu \nu} ,
\end{equation}
constraining $S$ to necessarily being not symmetric otherwise the trace $\Tr (S \varepsilon)$ vanishes and we would get $H _{\mu \nu} = 0$. In fact, to recover the modified Nambu-Goto action\eqref{eqn:modified-NG-action}, we require $(\Tr (S \varepsilon))^2 = 8$, thus $H_{\mu \nu} = G_{\mu \nu} / (- g)$.

>>>>

Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the auxiliary metrics $g_{c d}$ and $h_{c d}$:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{B P}}{\delta g^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}}
\end{multline}

\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}} \right) ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{B P}}{\delta h^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}}
\end{multline}
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} - \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}} \right) ,
\end{equation}
with
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If $S_{int} = 0$ and the auxiliary metrics $g_{a b}$ and $h_{a b}$ coincide with the induced metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, then the action\eqref{eqn:bimetric-Polyakov} reduces to
\begin{equation} \label{eqn:reduced-bimetric-action}
	S' _{B P} = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
\end{equation}
which, if $T' = - T k \Delta / 2$ and $h = g^{-1}$ becomes precisely the Nambu-Goto area corrected action\eqref{eqn:modified-NG-action}. The condition $h = g^{-1}$ can be achieved by
\begin{equation} \label{eqn:h=SgS}
	h_{a b} = S_{a c} g^{c d} S_{d b} ,
\end{equation}
where $S \in \mathrm{SL}(2 , \mathbb{C})$. The fact that we require $S = S^{\dagger}$ for $h$ to be real and symmetric restricts $S$ to be in the boosts sector of $\mathrm{SL}(2 , \mathbb{C})$. By requiring that the induced metric by $H_{\mu \nu}$ be equal to\eqref{eqn:h=SgS}, we get
\begin{equation} \label{eqn:H-from-SgS}
	\partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} = S_{a c} g^{c d} S_{d b}
\end{equation}
from which follows
\begin{equation}
	H_{\mu \nu} = \frac{1}{8 (- g)} (\Tr (S \varepsilon))^2 G_{\mu \nu} ,
\end{equation}
constraining $S$ to necessarily being not symmetric otherwise the trace $\Tr (S \varepsilon)$ vanishes and we would get $H _{\mu \nu} = 0$. In fact, to recover the modified Nambu-Goto action\eqref{eqn:modified-NG-action}, we require $(\Tr (S \varepsilon))^2 = 8$, thus $H_{\mu \nu} = G_{\mu \nu} / (- g)$.
